Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-02-06 paper.qmd
Updated with standardised error
added link brushing for MNIST

@@

error_df <- error_df |>
  mutate(sqrt_row_wise_tot_error = sqrt(row_wise_total_error))

@@

@@

@@

>>>>

tsne_plot_mnist_clust <- ggplot() + 
  geom_point(data = tsne_minst_scaled_temp,
             aes(
               x = tSNE1,
               y = tSNE2,
               colour = cluster
             ),
             alpha=0.2)+
  scale_color_manual(values=c('#f0f0f0', '#ff7f00')) +
  interior_annotation("a1", sc_ltr_pos_mnist) +
  theme(legend.position = "none")

@@

error_df <- error_df |>
  mutate(sqrt_row_wise_tot_error = sqrt(row_wise_total_error)) |>
  mutate(sqrt_row_wise_tot_error = standardize(sqrt_row_wise_tot_error))

@@

mnist_proj_tsne_model1_link <- projected_df |>
  ggplot(
    aes(
      x = proj1, 
      y = proj2,
      colour = cluster)) +
  geom_segment(
    data = model_df, 
    aes(
      x = proj1_from, 
      y = proj2_from, 
      xend = proj1_to, 
      yend = proj2_to), 
    color = "#000000",
    linewidth = 0.5,
    alpha = 0.5) +
  geom_point(
    size = 1.2,
    alpha = 0.5) +
  scale_color_manual(values = c("#d9d9d9",'#ff7f00')) +
  geom_segment(
    data=axes,
    aes(x=x1, y=y1, xend=x2, yend=y2),
    colour="grey70") +
  geom_text(
    data=axes,
    aes(x=x2, y=y2), 
    label=rownames(axes),
    colour="grey50",
    size = 2) +
  geom_path(
    data=circle, 
    aes(x=c1, y=c2), colour="grey70") +
  #coord_fixed() +
  xlim(c(-1.1, 0.9)) +
  ylim(c(-1.1, 0.9)) +
  interior_annotation("a2") +
  theme(
    legend.position = "none"
  )

@@

mnist_proj_tsne_model2_link <- projected_df |>
  ggplot(
    aes(
      x = proj1, 
      y = proj2,
      colour = cluster)) +
  geom_segment(
    data = model_df, 
    aes(
      x = proj1_from, 
      y = proj2_from, 
      xend = proj1_to, 
      yend = proj2_to), 
    color = "#000000",
    linewidth = 0.5) +
  geom_point(
    size = 1.2,
    alpha = 0.3) +
  scale_color_manual(values = c("#d9d9d9",'#ff7f00')) +
  geom_segment(
    data=axes, 
    aes(x=x1, y=y1, xend=x2, yend=y2), 
    colour="grey70") +
  geom_text(
    data=axes,
    aes(x=x2, y=y2), 
    label=rownames(axes),
    colour="grey50",
    size = 2) +
  geom_path(
    data=circle, 
    aes(x=c1, y=c2), colour="grey70") +
  coord_fixed() +
  xlim(c(-1, 1)) +
  ylim(c(-1, 1)) +
  interior_annotation("a3") +
  theme(
    legend.position = "none"
  )

@@

```{r}
#| label: fig-clust-mnist
#| fig-pos: H
#| fig-height: 5
#| fig-width: 15
#| out-height: 100%

tsne_plot_mnist_clust + mnist_proj_tsne_model1_link + mnist_proj_tsne_model2_link +
  plot_layout(ncol = 3)
```
